Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-05-21 Response.tex

            In short, the authors present a systematic method of generating optimal transfer orbits in the three-body problem.
            This paper provides a discrete optimal control formulation to generate the reachability set on a \Poincare section.
            % This results in an optimal solution rather than the suboptimal solution typical of direct optimal control methods which rely on coarse or suboptimal control parameterizations.
            % For example, a hybrid direct method may use a continuous control law developed from indirect optimal control theory while directly minimizing a cost function instead of solving the full two-point boundary value problem~\cite{ozimek2010a}.
            In addition, the use of a geometric integrators ensures numerical stability for long-duration orbit transfers and maintains this behavior with the addition of small magnitude control inputs.
            Our computation of the reachable set allows for a simple metric of defining optimal trajectories.
            We avoid the issues inherent in selecting a valid initial condition for optimization.
            Rather, we choose a state on the reachability set which minimizes the distance toward the desired target.
            We demonstrate these capabilities via two numerical examples simulating transfer trajectories in the Earth-Moon system.

        \end{correction}
\end{itemize}

\begin{itshape}
ISSUE 2: analysis/illustration (requires major revisions): 
My other highlighted area of concern with the original manuscript was the degree of (in)completeness in illustrating the method and its pros and cons.  I do not feel that the authors have done very much to improve this aspect of the paper beyond adding some caveats that feel a little half-hearted rather than properly contextualized discussions.  This aspect of the research remains a major shortcoming that must be addressed before publication.

While my request for improvements was itself not very specific, I had hoped that some of my other questions would reveal some areas of consideration for the authors.  Addressal/discussion of those questions furthermore needs to appear adequately in the paper, not just the rebuttal. Below I will try to sketch how these points of inquiry can lead to a more demonstrative analysis.
\end{itshape}
\newline\newline
Thank you for the comments and the additional suggestions to improve the manuscript. 
The main objective of the submitted manuscript is to construct a systematic approach to design low-thrust orbital maneuvers. 
It is motivated by the specific challenges that electric propulsion systems generate a minuscule level of thrust, and low-thrust orbital maneuvers rely on those effects accumulated over a long time period. 
It is quite cumbersome and challenging to apply numerical optimization tools or boundary value problem solvers successfully to low-thrust orbital design problems. 
We aim to provide more organized tools to mitigate such difficulties by explicitly considering the characteristics of the natural dynamics and utilizing geometric integrators exhibiting long-term numerical stability. 
The former is achieved by incorporating the control-free maneuvers obtained by the Poincare section in the invariant manifolds, and the latter is achieved by variational integrators. 
However, the proposed scheme does not guarantee any optimality in the constructed maneuvers. 
It is heuristically implied that the constructed orbital maneuver would require no-excessive control input, as it is essentially constructed by adjusting the control-free trajectory. 
In short,
\begin{itemize}
	\item[Pros] The proposed scheme utilizes the characteristics inherent in the three-body problem in constructing low-thrust orbital maneuvers in a systematic way. 
		This reduces the cumbersome process of guessing a \textit{good} set of initial parameters to make the direct application of optimization successful. 
	\item[Pros] The use of geometric integrators is particularly useful in capturing the long-term effects of low thrust in a computationaly efficient manner. 
	\item[Cons] While the proposed scheme generates orbital trajectories to the target with prescribed constraints, it does not guarantee any optimality. 
\end{itemize}
The conclusions section has been revised to summarize the above pros and cons of the proposed approach. 
\begin{correction}
In this paper, we construct a systematic approach which combines the concepts of reachability sets and \Poincare~sections to generate orbital transfers between planar periodic orbits in the three-body problem using low-thrust propulsion systems.
The \Poincare~section allows for trajectory design on a lower dimensional phase space thereby reducing the complexity and search space.
The approximation of the reachability set enables a simple methodology for the selection of \textit{good} initial parameters which will allow for convergence of the optimal control formulation.
The combination of these two concepts allows the engineer to capture the characteristics inherent in the three-body problem.
Additionally, we utilize geometric integrators to efficiently capture the long-term effects of low-thrust on the system dynamics.
Our approach enables the computation of orbital transfers within the three-body problem but does not guarantee optimality of the resulting transfer.
Instead, the resulting transfers will require no excessive control inputs as it is formulated as a deviation from the control-free trajectory.
The presented approach allows for a systematic method to determine and generate orbital transfers in the three-body problem using low-thrust proplusion.

There is additional research to extend these results to more general transfer scenarios in future work.
The incorporation of fourth body perturbations, such as the Sun in the Earth-Moon system, offers an additional method of increasing the reachable set with the combined use of the solar perturbation and low-thrust propulsion.
In addition, the assumed acceleration magnitude is currently beyond the capabilities of current electric propulsion systems and future research is aimed at investigating smaller magnitude control inputs.
Furthermore, this analysis did not consider the effect of variable mass on the optimal control solution.
This will result in a more complicated optimal control problem and is a focus of future research.
Finally, Lyapunov control theory, which has previously been applied to the two-body problem, is being investigated in the hope of designing closed loop control schemes for this three-body scenario~\cite{chang2002}.
The addition of attitude dynamics and realistic pointing constraints would also significantly improve the applicability of this work.

@@

    \subcaptionbox{Jacobi Energy: Energy history throughout the transfer.
    Each stage of the transfer serves to increase the energy towards the stable manifold. 
The final reachability set intersects the stable manifold and enables a large final manuever to the target orbit.\label{fig:jacobi_geo}}{\includegraphics[width=0.4\textwidth]{figures/geo_transfer/jacobi_energy.pdf}}

        \caption{Geostationary to \( L_1 \) periodic orbit transfer: Complete transfer from the geostationary orbit to the stable manifold.\label{fig:geo_transfer}}
\end{figure}
        \end{correction}
    \item 
        \begin{itshape}
            Following that thought, I have serious concerns about chaining this Poincare-based approach, as done in the second problem and as I previously asked about.  The authors' responded: "While the trajectories do return to the energy level of the Poincare section, there is a transfer of "energy" between the states of the vehicle." Frankly, this statement doesn't make sense to me.  I think that you are actually getting a very inefficient solution by forcing these repeated (and at fixed intervals) returns to the same energy level (again, plot the Jacobi time series and see if you can square it with your intuition).  Furthermore posing the problem as a transfer to the stable manifold kind of hamstrings the motivation of reducing transfer times.  Honestly, I think this second example should simply be axed.  If the first one is expanded enough to illustrate the problem fundamentals, it will be sufficient.  Conducting the same kind of analysis at a couple different rev counts would
            reveal the dimension that this second example added, and help reveal the limits of the approach under certain scenarios and thrust capabilities.
        \end{itshape}

		As pointed out by the reviewer, our response stating `..the trajectories do return to the energy level of the Poincare section..' is not correct. 
        Instead, the combination of several reachability sets does not force the system to return to a prescribed energy level.
        Each reachability set computation serves to maximize a distance metric, defined in a reduced phase space corresponding to the \Poincare section.
        The cost function is computed as the distance between the terminal states of the controlled and uncontrolled trajectories.
        The additional plots shown in both examples highlight the fact that the Jacobi energy is continuously changing as the control input is used to maneuver the vehicle towards the desired target states.

### 2018-05-21 manuscript.tex
Revise the conclusion

\section{Conclusions}\label{sec:conclusion}
In this paper, an optimal transfer process which combines concepts of reachability and \Poincare~sections is used to generate a transfer between planar periodic orbits in the three-body problem.
The \Poincare~section allows for trajectory design on a lower dimensional phase space and simplifies the process.
The indirect optimal control formulation directly solves for the state and costate vectors in the form of a two point boundary value problem which results in a lower number of design variables.
Direct optimal control techniques must rely entirely on the ability of the numerical optimization routine to determine a feasible solution and typically results in a much larger parameter set.
Our approach leverages the benefits of the reachability set, which encompass the maximum set of states achievable by the spacecraft over a fixed time horizon.
Using the reachability set on a \Poincare section reduces the dimensionality of the system and simplifies the analysis by avoiding the cost of a completely unmotivated exploration of the space.
However, the use of optimal control techniques leads to open loop trajectories that are not robust to model uncertainties or disturbances.

Furthermore, our approach relies heavily on the relative simplicity of the PCRTBP and this method is much more challenging for the non-planar case.

>>>>

\section{Conclusions}\label{sec:conclusion}
In this paper, we construct a systematic approach which combines the concepts of reachability sets and \Poincare~sections to generate orbital transfers between planar periodic orbits in the three-body problem using low-thrust propulsion systems.
The \Poincare~section allows for trajectory design on a lower dimensional phase space thereby reducing the complexity and search space.
The approximation of the reachability set enables a simple methodology for the selection of \textit{good} initial parameters which will allow for convergence of the optimal control formulation.
The combination of these two concepts allows the engineer to capture the characteristics inherent in the three-body problem.
Additionally, we utilize geometric integrators to efficiently capture the long-term effects of low-thrust on the system dynamics.
Our approach enables the computation of orbital transfers within the three-body problem but does not guarantee optimality of the resulting transfer.
Instead, the resulting transfers will require no excessive control inputs as it is formulated as a deviation from the control-free trajectory.
The presented approach allows for a systematic method to determine and generate orbital transfers in the three-body problem using low-thrust proplusion.
